### 2015-03-11 fundamentals/abs.tex
embeds abstract

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear,
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators
therefore couple complex systems such as nuclear process physics,
facility deployment, and material routing. However, most nuclear fuel cycle
simulators have not incorporated modern insights in simulation science and
software architecture that can enable more efficient, accurate, robust, and
validated analysis.

@@

>>>>

\begin{abstract}
As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear,
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators
therefore couple complex systems such as nuclear process physics,
facility deployment, and material routing. However, most nuclear fuel cycle
simulators have not incorporated modern insights in simulation science and
software architecture that can enable more efficient, accurate, robust, and
validated analysis.

@@

\end{abstract}
